\vspace{-1em}Guidance, Please! Towards a Framework for RDF-based Constraint Languages.

### 2015-07-28 paper/paper 2/dc-2015.tex
DC paper finalized

\begin{table}[H]
	\centering
	  %\caption{Constraint Type Specific Expressivity}
		\caption{Constraint Type Specific Expressivity of Constraint Languages}
	  \scriptsize
		\begin{tabular}{c|c|c|c|c}
      %\textbf{Expressivity Class} & $Expr(\overline{\mathcal{CT}_R})$ (42) & $Expr(\mathcal{CT}_R)$ (32) \\		
			\emph{DSP} & \emph{ReSh} & \emph{ShEx} & OWL 2 & \emph{SPIN} \\	
      \hline
			17.3 (14) & 25.9 (21) & 29.6 (24) & 67.9 (55) & \textbf{100.0} \textbf{(81)} 
		\end{tabular}
	\label{tab:constraint-type-specific-expressivity}
\end{table}

@@

The constraint type \emph{minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75}\footnote{Requirements are identified in the database by an R and a number, additionally an alphanumeric identifier is provided, in this case R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES. Online at: \url{http://lelystad.informatik.uni-mannheim.de/rdf-validation/?q=node/82}} can be instantiated to formulate the constraint that publications must have at least one author which must be a person. This constraint can be expressed as follows using different constraint languages:

@@

\paragraph{Consistent implementation.}
Even though SPIN provides a convenient way to represent constraints and to validate data according to these constraints, the implementation of a high-level constraint language still requires a tedious mapping to SPIN with a certain degree of freedom as to how a constraint violation is actually represented and how exactly the violation of the constraint is checked.
Our framework therefore provides a common ground that is solely based on the abstract definitions of the constraint types, as identified in our database. By providing a SPIN mapping
for each constraint type\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}\label{RDF-CV-2-SPIN}}, it is ensured that the details of the SPIN implementation are consistent irrespective of the constraint language and that the validation leads always to exactly the same results.

@@

Constraints of the \emph{irreflexive object properties (R-60)} constraint type ensure that no individual is connected by a given object property to itself \cite{Kroetzsch2012}. With the irreflexive object property constraint {\small\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists authorOf.Self$}}, e.g., one can state that individuals cannot be authors of themselves. When represented using the RDF-CV, the complex constraint aggregates three simple constraints (see Table \ref{tab:irreflexive-object-properties-as-complex-constraints}).

@@

\begin{table}[H]
  \scriptsize
  \sffamily
  \vspace{0cm}
	\caption{Irreflexive Object Properties as Complex Constraints}
	\label{tab:irreflexive-object-properties-as-complex-constraints}
	\centering
		\begin{tabular}{c|c|c|c|c|c}
      \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
$\exists$ authorOf.Self & authorOf & - & Self & existential quantification & - \\
$\neg$ $\exists$ authorOf.Self & - & - & $\exists$ authorOf.Self & negation & - \\
$\top$ & - & - & $\top$, $\neg$ $\exists$ authorOf.Self & sub-class & - \\
		\end{tabular}
\end{table}

@@

The \emph{Dublin Core Application Profile (DCAP)} and \emph{Bibframe Profiles} are approaches to specify \emph{profiles} for application-specific purposes. The term \emph{profile} is widely used to refer to a document that describes how standards or specifications are deployed to support the requirements of a particular application, function, community, or context. In the metadata community, the term \emph{application profile} has been applied to describe the tailoring of standards for specific applications. A \emph{Dublin Core Application Profile (DCAP)} \cite{DCMI-DCAP-2009} defines metadata records which meet specific application needs while providing semantic interoperability with other applications on the basis of globally defined vocabularies and models. The \emph{Singapore Framework for Dublin Core Application Profiles} \cite{DCMI-Singapore-2008} is a framework for designing metadata and for defining DCAPs. The framework comprises descriptive components that are necessary or useful for documenting DCAPs.

>>>>

\begin{table}[H]
	\centering
	  %\caption{Constraint Type Specific Expressivity}
		\caption{Constraint Type Specific Expressivity of Constraint Languages}
	  \scriptsize
		\begin{tabular}{c|c|c|c|c}
      %\textbf{Expressivity Class} & $Expr(\overline{\mathcal{CT}_R})$ (42) & $Expr(\mathcal{CT}_R)$ (32) \\		
			DSP & ReSh & ShEx & OWL 2 & SPIN \\	
      \hline
			17.3 (14) & 25.9 (21) & 29.6 (24) & 67.9 (55) & \textbf{100.0} \textbf{(81)} 
		\end{tabular}
	\label{tab:constraint-type-specific-expressivity}
\end{table}

@@

The constraint type \emph{minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75}\footnote{Requirements are identified in the database by an R and a number, additionally an alphanumeric identifier is provided, in this case \emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}. Online at: \url{http://lelystad.informatik.uni-mannheim.de/rdf-validation/?q=node/82}} can be instantiated to formulate the constraint that publications must have at least one author which must be a person. This constraint can be expressed as follows using different constraint languages:

@@

\paragraph{Consistent implementation.}
Even though SPIN provides a convenient way to represent constraints and to validate data according to these constraints, the implementation of a high-level constraint language still requires a tedious mapping to SPIN with a certain degree of freedom as to how a constraint violation is actually represented and how exactly the violation of the constraint is checked.
Our framework therefore provides a common ground that is solely based on the abstract definitions of the constraint types, as identified in our database. By providing a SPIN mapping
for each constraint type,\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}\label{RDF-CV-2-SPIN}} it is ensured that the details of the SPIN implementation are consistent irrespective of the constraint language and that the validation leads always to exactly the same results.

@@

Constraints of the \emph{irreflexive object properties (R-60)} constraint type ensure that no individual is connected by a given object property to itself \cite{Kroetzsch2012}. With the irreflexive object property constraint {\small\ms{$\top$ $\sqsubseteq$ $\neg$$\exists authorOf.Self$}}, e.g., one can state that individuals cannot be authors of themselves. When represented using the RDF-CV, the complex constraint aggregates three simple constraints (see Table \ref{tab:irreflexive-object-properties-as-complex-constraints}).

@@

\begin{table}[H]
  \scriptsize
  \sffamily
  \vspace{0cm}
	\caption{Irreflexive Object Properties as Complex Constraints}
	\label{tab:irreflexive-object-properties-as-complex-constraints}
	\centering
		\begin{tabular}{c|c|c|c|c|c}
      \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
$\exists$ authorOf.Self & authorOf & - & Self & existential quantification & - \\
$\neg$$\exists$ authorOf.Self & - & - & $\exists$ authorOf.Self & negation & - \\
$\top$ & - & - & $\top$, $\neg$$\exists$ authorOf.Self & sub-class & - \\
		\end{tabular}
\end{table}

@@

The \emph{Dublin Core Application Profile (DCAP)} and \emph{Bibframe Profiles} are approaches to specify profiles for application-specific purposes. The term \emph{profile} is widely used to refer to a document that describes how standards or specifications are deployed to support the requirements of a particular application, function, community, or context. In the metadata community, the term \emph{application profile} has been applied to describe the tailoring of standards for specific applications. A \emph{Dublin Core Application Profile (DCAP)} \cite{DCMI-DCAP-2009} defines metadata records which meet specific application needs while providing semantic interoperability with other applications on the basis of globally defined vocabularies and models. The \emph{Singapore Framework for Dublin Core Application Profiles} \cite{DCMI-Singapore-2008} is a framework for designing metadata and for defining DCAPs. The framework comprises descriptive components that are necessary or useful for documenting DCAPs.
